Fast, Scalable Phrase-Based SMT Decoding

### 2016-01-27 acl.2016/acl2016.tex
fixing segfault on thrud

The objective of decoding is to find the target translation with the maximum probability, given a source sentence. That is, for a source sentence $s$, the objective is to find a target translation $\hat{t}$ which has the highest conditional probability $p(t | s)$. Mathematically, this is written as:
\begin{equation}
\hat{t} = \arg \max_t p( t | s )
\label{eq:argmax-factored-trans}
\end{equation}
where the \emph{arg max} function is the search. The log-linear model generalizes the noisy channel model to include more component models and weighting each model according to the contribution of each model to the total probability. 
\begin{equation}
\label{eq:Log-Linear}
p(t | s) 	=  \frac{1}{Z} \exp ( \sum_m \lambda_m h_m ( t, s)^{} )
\end{equation}
where $\lambda_m$ is the weight, and $h_m$ is the feature function, or `score', for model $m$. $Z$ is the partition function which can be ignored for optimization. The log-linear formulation in phrase-based SMT uses log probabilities as feature functions, in addition to features which do not have a probabilistic interpretation. Typical feature functions include the log transforms of the target language model probability $p(t)$, and translation model probabilities, $p_{TM}(t|s) $ and $p_{TM}(s|t)$, which we have suffixed with $_{TM} $ to avoid confusion with the overall model probability $ p(t|s) $ and $ p(s|t)$.

@@

>>>>

The objective of decoding is to find the target translation with the maximum probability, given a source sentence. That is, for a source sentence $s$, the objective is to find a target translation $\hat{t}$ which has the highest conditional probability $p(t | s)$. Mathematically, this is written as:
\begin{equation}
\hat{t} = \arg \max_t p( t | s )
\label{eq:argmax-factored-trans}
\end{equation}
where the \emph{arg max} function is the search. The log-linear model generalizes Equation~\ref{eq:argmax-factored-trans} to include more component models and weighting each model according to the contribution of each model to the total probability. 
\begin{equation}
\label{eq:Log-Linear}
p(t | s) 	=  \frac{1}{Z} \exp ( \sum_m \lambda_m h_m ( t, s)^{} )
\end{equation}
where $\lambda_m$ is the weight, and $h_m$ is the feature function, or `score', for model $m$. $Z$ is the partition function which can be ignored for optimization.

@@

\subsection{Feature Functions}

Features functions are the $h_m$ in Equation~\ref{eq:Log-Linear}, calculating a score for each hypothesis which is then weighted and summed to give an overall score.

Standard feature functions in the phrase-based model include:
\begin{enumerate} 
  \item log transforms of the target language model probability $p(t)$, 
  \item log transforms translation model probabilities, $p_{TM}(t|s) $ and $p_{TM}(s|t)$, and word-based translation probabilities $p_w(t|s)$ and $p_w(s|t)$,
  \item log transforms of the lexicalized re-ordering probabilities,
  \item a distortion penalty
  \item a phrase-penalty,
  \item a word penalty,
  \item an unknown word penalty.
\end{enumerate}
%which we have suffixed with $_{TM} $ to avoid confusion with the overall model probability $ p(t|s) $ and $ p(s|t)$.

The first three feature functions frequently trained on data and require the feature to read the model from files. The other feature functions do not require model files.

\section{Experimental Setup}

We trained two phrase-based systems using the Moses toolkit, with standard settings. The first system was trained on most of the publicly available Arabic-English data from Opus (Jörg Tiedemann, 2012,) consisting of over 69 million parallel sentences, and tuned on a held out set. The second system was trained on the French-English Europarl corpus. The phrase-tables were then pruned, keeping only the top 100 entries per source phrase, according to $p(t|s)$. All models files were then binarized; thelanguage models were binaized using KenLM (???), the phrase table using Probing PT (???), lexicalized reordering model using the compact datastructure described in ???. These binary formats were choosen for their best-of-class multithreaded performance. Table~\ref{tab:model-files} gives details of the resultant sizes of the model files.
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& ar-en	& fr-en \\ \hline
Phrase table  	& 17 	& 5.8 \\
Language model 	& 3.1  	& 1.8 \\ 
Lex-re model	& 2.3	& 637MB \\ \hline
\end{tabular}
\end{center}
\caption{Model sizes in GB}
\label{tab:model-files}
\end{table}

For testing decoding speed, we used a subset of the training data, Table~\ref{tab:test-sets}. The two test set have differing characterics that we are interested in analyzing, ar-en have short sentences while fr-en have overly long sentences.

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& ar-en	& fr-en \\ \hline
\# sentences  	& 800k 	& 200k \\
\# words 	& 5.8m 	& 5.9m \\ 
\Avg words/sent	& 7.3	& 29.7 \\ \hline
\end{tabular}
\end{center}
\caption{Model sizes in GB}
\label{tab:test-sets}
\end{table}

Where we need to compare the model score of the algorithms, we used a held out set; ??? for ar-en and ??? for fr-en.

Standard Moses phrase-based configurations are used, except that we use the cube-pruning algorithm (???) with a pop-limit of 400, rather than the basic phrase-based algorithm. The cube-pruning algorithm is often employ by users who are sensitive to decoding speed as it gives them the ability to trade speed with translation quality with a simple pop-limit parameter.

\section{Results}
